\section{Pivot Transitions}
\label{sec:transitions/pivot}

Some practice with manuals will assist with this technique.
Manuals drills may be found in \ref{sec:sticky/manuals}.


The goal of a pivot transition is to flip position using only the front or back two wheels on each skate.  

\subsection{Forwards Pivot Transitions}
\label{sec:transitions/pivot/forwards}
The skater begins in a staggered stationary position.
The skater should then perform a front manual on both feet, and be comfortable holding that position. 

The skater should then be able to turn both feet either clockwise or anti-clockwise while holding the manual.
After turning 180 degrees and placing their heels the skater will have performed a pivot transition. 

The motion for performing this transition while moving is identical.  

\subsection{Backwards Pivot Transitions}
\label{sec:transitions/pivot/backwards}

Unlike the forwards transition, this one requires backwards manuals on both wheels.
It is important to note that when performing back-wheel manuals that there is no support for the skater should they begin to fall backwards. 
For this reason a staggered stance should be maintained.

While turning there will be a moment when the skaters wheels are in line and the stance is no longer staggered, it is best not to hold this position. 

The skater begins in a staggered stationary position.
The skater should then perform a front manual on both feet, and be comfortable holding that position. 

The skater should then be able to turn both feet either clockwise or anti-clockwise while holding the manual.
After turning 180 degrees and placing their heels the skater will have performed a pivot transition. 

The motion for performing this transition while moving is identical.  

\subsection{One Foot Forwards Pivot Transitions}
\label{sec:transitions/pivot/one_foot_forwards}
For this technique it is imperative that the skater keeps their knee bent.

Now that the other leg is no longer an issue, we are free to pivot transition either clockwise or anti-clockwise.

\subsection{One Foot Backwards Pivot Transitions}

