\subsection{Engaged Spins}
\label{drill:jammer_movement/momentum_jukes/engaged_spins}

This drill is about spinning out of an engagement with a blocker.


Begin with a jammer and blocker pair, the jammer should be moving forwards while the blocker is steering them towards a line.

At arbitrary intervals the jammer should spin in a circle using their edges to flip their direction of travel. 

While it seems tempting to perform the spin on the line - at that stage the blocker is aware that the jammer is out of options - the jammer should try to spin before reaching lanes 1 or 4.     

As this involves an edgework spin, it may only be performed at medium speed, it is not suitable for approaching a wall at high speed.

\vspace{0.15cm}


{\it Extensions: Cut Track}
By increasing the speed of the initial lateral movement, and throwing a hip hit at the end of the spin the goal is to push the blocker off the track using their own momentum.


\vspace{0.15cm}

{\it Extensions: Combos}
This can also be the first move in a combo:

{\it Step 1a: }
The jammer disengages and moves behind the blocker, passing them.


{\it Step 1b: }
The the jammer completes a full $360\deg$ spin and continues their trajectory while the blocker has expected as single turn. 


{\it Step 1c: }
The jammer performs a drop step out of the spin, disengaging hips and returning to their original path while the blocker moves to cover their path after the spin.


{\it Step 1d: }
The jammer performs a jab juke in the direction of motion after the spin, further forcing the blocker out of position before disengaging and passing the blocker. 

