\section{Skating to Toe Stops and Back}
\label{sec:toe_stop/skating_to_toe}
% Pi

This section deals with alternating between skating, running on toe-stops and moving back to skating.

The primary difficulty with this skill is that toe-stops are typically angled such that jumping onto them while rolling without first matching momentum will result in the skater falling over.    
This angling also means that this skill is easier to practice backwards.


All of the following drills should be attempted at low speed first. 
If the skater is not comfortable moving at the required speed when starting on toe stops, they should not attempt to move onto toe stops from that speed when rolling.  

\subsection{Skating Backwards}
Skate backwards, hop onto toe stops for a couple of steps, resume skating backwards.
This is easier than the forwards version as the toe stops are already angled backwards. 

If the skater needs to bail out from this movement they can drop onto their toe stops and come to a stop. 


\subsection{Sideways}
Similarly to the backwards version, this can also be performed sideways while avoiding angling issues with toe-stops.  

From a side surf, incorporate a small jump landing on toe stops.
The skater then uses their existing momentum to perform a side shuffle or a grapevine on toe stops.   
They then return to a side surf.

If the skater is concerned by the sideways momentum on their toe-stops, the first toe-stop steps may be accompanied by a partial transition for greater stability.  


\subsection{Skating Forwards}
The hardest of the three. 
Care must be taken to place the toe-stops at the correct angle while moving forwards. 
Leaning forwards will help with this, as will maintaining momentum. 


