\section{Backwards Sticky Skating}
\label{sec:sticky/backwards}

The basic skills here are similar to those in \Cref{sec:sticky/eggshells} except now we are going backwards. 

This necessitates a few minor changes.
The first being that our weight has moved from just in front of the back truck, to just behind the front truck of the skate. 
Instead of steering with the front of the skate, we now steer with the back.

Additionally, as going backwards involves the skater not seeing the direction in which they are skating, it is strongly advised to look over one shoulder - typically towards the inside of the track.     

The drills here are near identical to the front facing eggshells. 

\subsection*{Developmental Drill: On the Spot}
\label{drill:sticky/backwards/spot}

This drill is about getting comfortable enough with the edges of the skates to perform the motions required for an eggshell.   

It also assists in shifting weight from the front to the back of the skate. 

Starting from a stopped position, the skater should attempt to perform one eggshell motion forwards, then the same motion backwards, ending up in their starting position.  


\subsection*{Development Drill: One Edge at a Time}
\label{drill:sticky/backwards/one_edge}

This is a variant drill for regular sticky skating. 
It's targeted skaters who are comfortable moving around on skates, but may be compensating for not fully developed edge-work in sticky skating.
Breaking down the motions and forcing each to pull their own weight should show this up quite quickly.

The core idea of the drill is to only use a single movement for propulsion.  

One leg should be stationary, the other should begin on the in, push out as you would when sticky skating then lift the leg at the end of the motion.  
Place the leg back on the inside and repeat. 

For the alternative motion the leg should start on the out and pull in.   

Avoid large flicks and other crossover-like motions.    

Repeat the following skating forwards and backwards. 
\begin{itemize}
    \item 1$\times$ lap right leg pushing out, left leg stationary  
    \item 1$\times$ lap left leg pushing out, right leg stationary 
    \item 1$\times$ lap right leg pulling in, left leg stationary 
    \item 1$\times$ lap right leg pulling in, right leg stationary 
\end{itemize}

To put the motions back together:
\begin{itemize}
    \item 2$\times$ laps regular sticky skating. 
\end{itemize}


\subsection*{Warm Up Drill: Backwards Eggshells and Variants}
\label{drill:sticky/backwards/warm_up}

This is a collection of egg-shell drills that can be performed as part of a warm-up. 

\begin{itemize}
    \item Backwards eggshells  
    \item Wide eggshells
    \item Eggshells with alternating legs crossing in front and behind (figure 8) 
    \item Short fast eggshells, skates coming into proximity 
    \item Squat position eggshells, skates only sliding    
\end{itemize}
