\section{Manuals}
\label{sec:sticky/manuals}

Manuals are a dance-skating technique involving skating or balancing on two wheels on each skate.   
Typically these are either the front or back two wheels, but they may also be the side wheels.

Manuals are not technically a necessary derby skill, but are required for some variant skills (such as pivot transitions in \Cref{sec:transitions/pivot}).    


\subsection*{Developmental Drill: Heel-Toe}

Start in a split stance. Front wheel balances on the heel, the back wheel balances on the toe. 
Simply practice adopting this stance and dropping back into the stagger.

\subsection*{Developmental Drill: Manual Pull}

This drill improves egg shells as well as generates force using fewer than four wheels on the ground.  

Adopt a split stance. 
Leave all four wheels of the back leg on the ground.  
On the front leg use either a heel or a toe manual.  

Perform eggshells using just the front or back two wheels of the front skate. 


\subsection*{Front-Back Balancing}

The easiest manual to perform is to take a split stance and balance on the front wheels of the back foot, and the back wheels of the front foot. 

{\bf Progressions:}
The tighter the split stance the more difficult the balancing act.
Bringing legs closer together will increase the difficulty of the activity.


\subsection*{Sideways Balancing}
This technique runs the risk of rolling and ankle badly.

The easiest form is to balance on the outside wheels of each foot.

A rolling version of this manual is to raise the non-engaged edges during weaving or carving.



\subsection*{Switching}
Using almost any manual configuration, switch legs without dropping the manual.

Do not attempt this with both feet using heels.


\subsection*{Manual Eggshells}

Perform eggshells without dropping out of a manual.
