\section{Side Surfing}
\label{sec:one_foot/side_surf}

Side surfing is a close relative of one footed skating - most of the skater's weight is distributed to a single foot.

The core technique is to load all the skater's weight into their front leg (leaning may help) while keeping the back leg on the ground in an open position.

{\it Common Pitfall:} If the skater is spinning as they attempt to perform a side-surf it is likely that they are trying to centre their weight.  
Moving their weight to the front leg should assist with this.

\subsection*{Developmental Drill: Circling}

When developing side-surfing skaters may discover that they don't have the hip flexibility to reach the required angle for a proper side surf.   

Instead the skaters may opt for a smaller hip angle and instead work in small circles. 

\begin{itemize}
\item Take a stance with the hips open to a comfortable angle.
\item Pick a `forwards direction' and lock that leg in. 
\item Perform egg-shell movements with the back leg to generate momentum. 
\item Steer in a circle with the forwards leg.
\end{itemize}


If the skater is cleared for contact, it may be helpful to circle while hold hands with another more experienced skater when performing this drill.  
The other skater can provide the initial momentum which will help with developing proper form and hip angling.  

\subsection*{Stroked Side Surfing}

Rather than holding the position, use the back leg to provide propulsion by lifting and performing a `stroke'.    

{\it Progressions:}
\begin{itemize}
\item Perform multiple strokes before resuming forwards skating.  
\item Alternate the facing of the side surf and stroke accordingly. 
\end{itemize}


\subsection*{Backwards Weighted Side Surfing}

Side surfing can also be performed near identically with the weight in the back foot. 

The skater should begin skating forwards and lift and place their rear foot to enter into a side surf.
The skater may initially weight their front leg. 
The skater should then transfer their weight to their back leg while maintaining the side surf.
They should be able to demonstrate this by lifting their front leg as they skate.

This technique is useful for a number of loaded jumps.
