\subsection*{Developmental Drill Sequence: Reconstruction}
\label{drill:weaves/developmental}

After eggshells, developing skaters may not yet have sufficient control to be doing different things with each leg.       

This drill sequence tries to break down and re-build weaves as a series of simple motions.   

\subsubsection*{Serial D Cuts}
Begin with locking one leg in the forwards position.
Perform an `eggshell' like maneouvre with the free leg, starting by {\bf pushing out} then pulling in.
Swap which leg is locked, and repeat.


\subsubsection*{Turning}
As with the previous component, but now bring the free foot further through the turn such that the skater turns with each motion rather than simply rolling forwards. This will require bringing the inside leg through the turn slightly.    
Focus on turning the hips to face and pull through the turn.

\subsubsection*{Internal D Cuts}
Begin with locking one leg in the forwards position.
Perform an `eggshell' like maneouvre with the free leg, starting by {\bf pulling in}, then pushing out.
Swap which leg is locked, and repeat.

\subsubsection*{Internal Turning}
As with the previous component, but now bring the free foot further through the turn such that the skater turns with each motion rather than simply rolling forwards. This will require bringing the outside leg through the turn slightly.    
Focus on turning the hips to face and pull through the turn.

\subsubsection*{Composition}
We now combine the motions of each foot, hopefully having keyed this in part to the hip movements.   
The goal here is to get the synchronisation and rhythm down having developed the components. 


